The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-01-30 paper/main.tex
minor text edits

\newcommand{\pp}{\mathcal{P}}
\newcommand{\ps}{\mathcal{S}}
\renewcommand{\a}{_{\rm a}}
\newcommand{\s}{_{\rm s}}
\newcommand{\p}{_{\rm p}}
\renewcommand{\d}{_{\rm d}}
\begin{document}

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
Wide-field surveys for transiting planets, such as the NASA {\it Kepler}
and {\it TESS} missions, are usually conducted without knowing which stars
are actually binaries. Unresolved and unrecognized binary stars give rise to 
systematic errors in planet occurrence rates, including misclassified planets 
and miscounts in the number of searched stars. The individual errors can have 
different signs, making it difficult to anticipate the net effect on planet 
occurrence rates. Here we use simplified models of signal-to-noise limited 
transit surveys to try and clarify the situation. We derive a formula for the 
apparent occurrence rate density measured by an observer who falsely assumes 
all stars are single. The formula depends on the binary fraction; the 
mass function of the secondary stars; and the true occurrence of planets 
around primaries, secondaries, and single stars. It also takes into account 
the Malmquist bias by which binaries are over-represented in flux-limited 
samples. Application of the formula to an idealized {\it Kepler}-like survey 
shows that for planets larger than $2r_\oplus$, the net systematic error is of 
order 10\%. For smaller planets the errors are potentially larger: the 
occurrence of Earth-sized planets could be overestimated by as much as a 
factor of two. One consequence is that unrecognized binaries cannot account 
for the apparent discrepancy between the hot Jupiter occurrence rates measured 
by transit and RV surveys. We also demonstrate that if high-resolution imaging 
reveals a transit host star to be a binary, the planet is usually more likely 
to orbit the primary star than the secondary star.
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

To clarify our terminology, we define an ``apparent planet radius'', $r\a$, as 
the radius that one would infer from a transit signal under the assumption 
that the host star is single.
The observed transit depth is given by the ratio of the apparent planet
radius and the apparent stellar radius, $R\a$:
\begin{equation}
\delta_{\rm obs}
= \left(\frac{r\a}{R\a}\right)^2
= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
        sys}},
\label{eq:delta_obs_general} 
\end{equation}
where $r$ is the planet radius, $R_{\rm host}$ ($L_{\rm host}$) is the 
host star's radius (luminosity), and $L_{\rm sys}$ is the 
entire system's luminosity.
For the example at hand, $R_{\rm host} = R$, since all stars have the same 
size. In single star systems we have $r=r\a=r\p$. In twin binaries, 
$r\a=r\p/\sqrt{2}$, since $L_{\rm sys}=2L$.

@@

We can write similar equations for the binaries.
First though, we define a ratio $\mu \equiv N_\star^{\rm b}(r\a) / 
N_\star^0(r\a)$ 
between the number of searchable binary systems and the number of searchable 
singles at any $r\a$.
This quantity is useful because although $N_\star^{\rm b}$ and $N_\star^0$ vary
as a function of the observed transit depth, $\mu$ remains fixed.
Applying this definition, at $r\a=r\p/\sqrt{2}$, some detections will come 
from primaries,
\begin{equation}
n_{\rm det}^1(r\a) =
\mu N_\star^0(r\a) Z_1 p_{\rm tra}
\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
and some from secondaries,
\begin{equation}
n_{\rm det}^2(r\a) = 
\mu N_\star^0(r\a) Z_2 p_{\rm tra}
\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
where $Z_1$ is the number of planets per primary, $Z_2$ is the number of 
planets per secondary, and $p_{\rm tra}$ is the same for identical stars.
For twin binaries, Equation~\ref{eq:N_searchable_prop} gives $\mu = 
2^{3/2} n_{\rm b}/n_{\rm s}$, where $n_{\rm b}$ is the number density of 
binaries in a volume-limited sample.

@@

To assess the severity of these errors, we must assume both a binary fraction, 
and also the true number of planets per single, primary, and secondary star 
($Z_0,Z_1,Z_2$).
For the former,~\citet{raghavan_survey_2010} found a multiplicity 
fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$.
By multiplicity fraction, they meant ``fraction of systems in a volume-limited 
sample that are multiple'', which we simplistically take to be fraction of 
systems in a volume-limited sample that are binaries:
\begin{equation}
{\rm binary\ fraction} \equiv \frac{n_b}{n_s + n_b} = 0.44,
\end{equation}
Of course not all of these are binaries are close to being ``twin'' binaries 
as we have assumed in our simple calculation.
Perhaps only a tenth of them have pairs of stars close enough
in their basic properties to produce errors as significant as those
we have been considering.  Thus, an appropriate estimate
for the binary fraction is of order $0.05$.
The ratio of the apparent to single star rate densities,
\begin{equation}
X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} \right|_{r\a 
    \rightarrow r},
\end{equation}
can then be thought of as a ``correction factor''.
At the true planet radius, $X_\Gamma(r\p)=1/(1+\mu)$.
This yields a correction $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 
0.05~(0.10).
All together the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is characteristic
of many of our more complicated models, as well.

An alternative assumption is that secondaries do not host planets. In that 
case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
planet radius becomes $X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.
This gives a correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
While the secondaries certainly do have planets, 
the fact that $\Gamma\a/\Gamma_0$ is sensitive to the relative number 
of planets per single, primary, and secondary will become important as we 
proceed.

@@

A simple extension to the previous example will help us further distinguish 
the detected populations.
Consider now a universe that is the same in every respect to that of 
Section~\ref{sec:model_1}, except that half of planets have true radii $r\p$, 
while the other half have true radii $r\p/\sqrt{2}$.
The true rate densities are
\begin{equation}
\Gamma_i(r) = \frac{Z_i}{2} \left[
\delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
\right], \quad {\rm for}\  i \in \{ 0,1,2 \},
\end{equation}
where as before $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
secondaries, and the $Z_i$'s are the number of planets per star of each type.

Following an identical line of reasoning as in Section~\ref{sec:model_1}, the 
apparent rate density can be written
\begin{align}
\notag
\Gamma\a(r\a) &=
\frac{1}{2(1+\mu)} \left[
Z_0 \cdot \delta(r\a - r\p)
+
\left[Z_0 + \mu (Z_1 + Z_2)
\right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad+
\left.
\mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
\right].
\label{eq:two_radii_twins}
\end{align}
The important qualitative point of this equation is that at $r\a = 
r\p/\sqrt{2}$, two populations contribute.
The first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
binaries with $r=r\p$.
Both populations are detected out to the same maximum searchable distance.
Just as with Equation~\ref{eq:apparentlysearchable_to_searchable}, we benefit 
from a cancellation of $N_\star^0(r\a)$ terms, leaving only the $\mu$ weights.

@@

Given this laundry-list of assumptions, a general formula for the apparent 
rate density follows:
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma_0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int_0^1 \mathrm{d}q \,
       \frac{f(q)}{\mathcal{A}^3}\cdot
       \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int_0^1 {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
    \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\},
\label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}$ is the volume-limited binary fraction, 
and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms for 
primaries [secondaries], whose functional dependences are omitted for 
notational simplicity.
The dilution terms can be written
\begin{equation}
\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
= (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
            sys}(M\a, q)} }
= q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
former are more general).
The rate densities depend on both apparent radius and mass 
because even if the primaries and singles were to have fixed
mass, the mass of secondaries would vary, and so this dependence cannot be 
immediately omitted.

@@

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu({\rm BF},M\a)$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distance for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Equation~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\,\mathrm{d}q.
\label{eq:mu_general}
\end{equation}
If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this simplifies to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q,
\label{eq:mu_power_laws}
\end{equation}
which may be written in a closed form using the hypergeometric function.

@@

\section{Realistic Star and Planet Distributions}
\label{sec:more_complicated}
The following section applies our general equation for the apparent rate 
density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
regimes 
of observational interest.
In general, we will write the rate density for each type of star, 
$\Gamma_i(r)$, as the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where as always, $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
The shape function is normalized to unity.
The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
over all planetary radii. In other words, they are number of planets per 
single, primary, or secondary star.
This section will consider the effects of varying both $f_i(r)$ and also the
relative values of the $Z_i$'s.

@@

\subsubsection{Twin binaries}
We begin introducing realism by keeping all binaries as twins, but letting the 
radius distribution of planets vary.
Specifically, we take
\begin{equation}
\Gamma_i(r) = Z_i f(r) = Z_i r^\delta/\mathcal{N}_r,
\end{equation}
for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape function's 
normalization.
The resulting apparent rate density is quite similar to that of the twin 
binary, fixed-planet case (Equation~\ref{eq:model_1_apparent_rate_density}), 
except 
for a slightly different radius dependence and normalization:
\begin{equation}
\Gamma\a(r\a) = \frac{r\a^\delta}{\mathcal{N}_r} \left[
\frac{Z_0}{1+\mu}
+
2^{\frac{\delta+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
\right)
\right].
\label{eq:model5_apparent_rate_density}
\end{equation}
As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} {\rm BF}/(1-{\rm BF})$.
If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
density for singles becomes quite simple:
\begin{align}
\left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r}
&=
\frac{1 + 2^{\frac{\delta+3}{2}}\mu}{1 + \mu}.
\label{eq:power_law_correction}
\end{align}
For the case of ${\rm BF}=0.1$, $\mu\approx 0.153$. Taking $\delta=-2.92$ from 
\citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
1.004$.
In other words, the apparent rate density is an {\it over}estimate compared to 
the rate density of single stars, with a relative difference $\delta \Gamma_0 
= |\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
This is quite a small effect!
Note though that it could change if the $Z_i$'s are not equal.
Also, the power law radius distribution $f(r) \propto r^\delta$ diverges for 
$\delta < 0$; \citet{howard_planet_2012}'s results indicate that this
approximation is good for $r\a\gtrsim 2r_\oplus$.
Similarly, it is nonsensical for $f(r)$ to be finite above some upper radius 
limit $r_u$, perhaps around $\approx 24r_\oplus$, based on the most inflated 
hot Jupiters.
An upper cut-off of $r_u$ would lead to smaller values of $\Gamma(r\a)$ 
down to $r_u/\sqrt{2}$, compared to an intrinsic power law without the cut-off.
We are not particularly interested in this effect; there are better 
models for hot Jupiter occurrence rates that we will discuss in 
Section~\ref{sec:further_models}.
If the assumptions behind this model (listed in 
Section~\ref{sec:general_formula}) are at all applicable in real transit surveys, 
this suggests that for $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$, 
binarity's impact on derived occurrence rates is quite small.

@@

We are mostly interested in the apparent rate density's radius dependence.
Marginalizing Equation~\ref{eq:general_Gamma_a} over apparent stellar mass, we 
find
that when $Z_0=Z_1=Z_2$,
\begin{align}
X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r} \\
&=
\notag
\frac{1}{1+\mu}
\left[1 + \frac{1}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}\times 
\left(
\int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
\right.
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
\left.\left.
\int_0^1 {\rm d}q\,q^{\beta+\delta+\frac{5}{3}} 
(1+q^\alpha)^{\frac{3}{2}}
(1+q^{-\alpha})^{\frac{\delta+1}{2}}
\right)\right],
\label{eq:powerlaw_vary_binary}
\end{align}
where $\gamma$ does not appear because of the marginalization over $M\a$.
For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give 
$(\ldots)\approx 
1.50249$. %171211_model_integrals.nb
For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
relative difference between the apparent rate density and the rate density 
around singles is 4.8\%.
This indicates that considering only twin binaries gave us correct 
intuition: for a power-law radius distribution 
($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
number of planets orbiting singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level.

>>>>

\newcommand{\pp}{\mathcal{P}}
\newcommand{\ps}{\mathcal{S}}
\renewcommand{\a}{_{\rm a}}
\newcommand{\s}{_{\rm s}}
\newcommand{\p}{_{\rm p}}
\renewcommand{\d}{_{\rm d}}
\renewcommand{\b}{_{\rm b}}
\begin{document}

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
Wide-field surveys for transiting planets, such as the NASA {\it Kepler}
and {\it TESS} missions, are usually conducted without knowing which stars
are actually binaries. Unresolved and unrecognized binary stars give rise to 
systematic errors in planet occurrence rates, including misclassified planets 
and miscounts in the number of searched stars. The individual errors can have 
different signs, making it difficult to anticipate the net effect on planet 
occurrence rates. Here we use simplified models of signal-to-noise limited 
transit surveys to try and clarify the situation. We derive a formula for the 
apparent occurrence rate density measured by an observer who falsely assumes 
all stars are single. The formula depends on the binary fraction; the 
mass function of the secondary stars; and the true occurrence of planets 
around primaries, secondaries, and single stars. It also takes into account 
the Malmquist bias by which binaries are over-represented in flux-limited 
samples. Application of the formula to an idealized {\it Kepler}-like survey 
shows that for planets larger than $2r_\oplus$, the net systematic error is of 
order 10\%. For smaller planets the errors are potentially larger: the 
occurrence of Earth-sized planets could be overestimated by as much as a 
factor of two. One consequence is that unrecognized binaries cannot account 
for the apparent discrepancy between the hot Jupiter occurrence rates measured 
by transit and RV surveys. We also show that if high-resolution imaging 
reveals a transit host star to be a binary, the planet is usually more likely 
to orbit the primary star than the secondary star.
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

To clarify our terminology, we define ``apparent properties'' as the 
properties that one would infer about a system under the assumption that the 
host star is single. For instance, the  ``apparent planet radius'', $r\a$, is
the planet radius that one would infer from a transit signal, 
assuming that the host star is single.
The observed transit depth is given by the ratio of the apparent planet
radius and the apparent stellar radius, $R\a$:
\begin{equation}
\delta_{\rm obs}
= \left(\frac{r\a}{R\a}\right)^2
= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
        sys}},
\label{eq:delta_obs_general} 
\end{equation}
for $r$ the planet radius, $R_{\rm host}$ ($L_{\rm host}$) the 
host star's radius (luminosity), and $L_{\rm sys}$ the 
entire system's luminosity.
In the example at hand, $R_{\rm host} =R\a = R$, since all stars have the same 
size. For single star systems we have $r=r\a=r\p$. In twin binaries, 
$r\a=r\p/\sqrt{2}$, since $L_{\rm sys}=2L$.

@@

We can similarly compute the number of planet detections from binaries.
First though, we define a ratio $\mu \equiv N_\star^{\rm b}(r\a) / 
N_\star^0(r\a)$ 
between the number of searchable binary systems and the number of searchable 
singles at any $r\a$.
This quantity is useful because although $N_\star^{\rm b}$ and $N_\star^0$ vary
as a function of the observed transit depth, $\mu$ remains fixed.
Applying this definition, at $r\a=r\p/\sqrt{2}$, some detections will come 
from primaries,
\begin{equation}
n_{\rm det}^1(r\a) =
\mu N_\star^0(r\a) Z_1 p_{\rm tra}
\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
and some from secondaries,
\begin{equation}
n_{\rm det}^2(r\a) = 
\mu N_\star^0(r\a) Z_2 p_{\rm tra}
\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
where $Z_1$ is the number of planets per primary, $Z_2$ is the number of 
planets per secondary, and $p_{\rm tra}$ is the same for identical stars.
For twin binaries, Equation~\ref{eq:N_searchable_prop} gives $\mu = 
2^{3/2} n_{\rm b}/n_{\rm s}$, where $n_{\rm b}$ is the number density of 
binaries in a volume-limited sample.

@@

To assess the severity of these errors, we must assume both a binary fraction, 
and also the true number of planets per single, primary, and secondary star 
($Z_0,Z_1,Z_2$).
For the former,~\citet{raghavan_survey_2010} found a multiplicity 
fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$.
By multiplicity fraction, they meant ``fraction of systems in a volume-limited 
sample that are multiple'', which we simplistically take to be fraction of 
systems in a volume-limited sample that are binaries:
\begin{equation}
{\rm binary\ fraction} \equiv \frac{n\b}{n\s + n\b} = 0.44,
\end{equation}
Of course not all of these are binaries are close to being ``twin'' binaries 
as we have assumed in our simple calculation.
Perhaps only a tenth of them have pairs of stars close enough
in their basic properties to produce errors as significant as those
we have been considering.  Thus, an appropriate estimate
for the binary fraction is of order $0.05$.
The ratio of the apparent to single star rate densities,
\begin{equation}
X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} \right|_{r\a 
    \rightarrow r},
\end{equation}
can then be thought of as a ``correction factor''.
At the true planet radius, $X_\Gamma(r\p)=1/(1+\mu)$.
This yields a correction $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 
0.05~(0.10).
All together the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is characteristic
of many of our more complicated models, as well.

An alternative assumption is that secondaries do not host planets. In that 
case, the correction to the rate density at the true planet radius becomes 
$X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.
This gives a correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
Although the secondaries certainly should have planets, 
the fact that $\Gamma\a/\Gamma_0$ is sensitive to the relative number 
of planets per single, primary, and secondary will also become
important as we proceed.

@@

A simple extension to the previous example helps distinguish 
between the apparent and underlying planet populations.
Consider now a universe that is the same as that of 
Section~\ref{sec:model_1}, except that half of planets have radii $r\p$, 
while the other half have radii $r\p/\sqrt{2}$.
The rate densities are
\begin{equation}
\Gamma_i(r) = \frac{Z_i}{2} \left[
\delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
\right], \quad {\rm for}\  i \in \{ 0,1,2 \},
\end{equation}
where as before $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
secondaries, and the $Z_i$'s are the number of planets per star of each type.

Following an identical line of reasoning as in Section~\ref{sec:model_1}, the 
apparent rate density can be written
\begin{align}
\notag
\Gamma\a(r\a) &=
\frac{1}{2(1+\mu)} \left[
Z_0 \cdot \delta(r\a - r\p)
+
\left[Z_0 + \mu (Z_1 + Z_2)
\right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad+
\left.
\mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
\right].
\label{eq:two_radii_twins}
\end{align}
There are now three different sizes of detected planets.
The important qualitative point is that at $r\a = 
r\p/\sqrt{2}$, two populations contribute.
The first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
binaries with $r=r\p$.
Both populations are detected out to the same maximum searchable distance.
Just as with Equation~\ref{eq:apparentlysearchable_to_searchable}, we benefit 
from a cancellation of $N_\star^0(r\a)$ terms, leaving only the $\mu$ weights.
Generally, at any given apparent radius, there will be contributions
from both single, primaries, and secondaries~---~but the relative weights
between these contributions will depend on the underlying occurrence rates.

@@

Given this laundry-list of assumptions, a general formula for the apparent 
rate density follows:
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma_0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int_0^1 \mathrm{d}q \,
       \frac{f(q)}{\mathcal{A}^3}\cdot
       \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int_0^1 {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
    \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\},
\label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}=n\b/(n\s+n\b)$ is the volume-limited binary fraction, 
and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms for 
primaries [secondaries], whose functional dependences are omitted for 
notational simplicity.
The dilution terms can be written
\begin{equation}
\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
= (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
            sys}(M\a, q)} }
= q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
former are more general).
The rate densities depend on both apparent radius and mass 
because even if the primaries and singles were to have fixed
mass, the mass of secondaries would vary, and so this dependence cannot be 
immediately omitted.

@@

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu({\rm BF},M\a)$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distance for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Equation~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\,\mathrm{d}q.
\label{eq:mu_general}
\end{equation}
If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this simplifies to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q,
\label{eq:mu_power_laws}
\end{equation}
which can also be rewritten using the hypergeometric function.

@@

\section{Realistic Star and Planet Distributions}
\label{sec:more_complicated}
This section applies our general equation for the apparent rate 
density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
regimes of observational interest.
In what follows, we will write the rate density for each type of star, 
$\Gamma_i(r)$, as the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
The shape function is normalized to unity.
The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
over all planetary radii. In other words, they are number of planets per 
single, primary, or secondary star.
We want to consider the effects of varying not only $f_i(r)$ but also the
relative values of the $Z_i$'s.

@@

\subsubsection{Twin binaries}
We begin introducing realism by keeping all binaries as twins, but letting the 
planet radius distributions vary.
Specifically, we take
\begin{equation}
\Gamma_i(r) = Z_i f(r) = Z_i r^\delta/\mathcal{N}_r,
\end{equation}
for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape function's 
normalization.
The resulting apparent rate density is 
\begin{equation}
\Gamma\a(r\a) = \frac{r\a^\delta}{\mathcal{N}_r} \left[
\frac{Z_0}{1+\mu}
+
2^{\frac{\delta+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
\right)
\right],
\label{eq:model5_apparent_rate_density}
\end{equation}
which is quite similar to the twin binary, fixed-planet case 
(Equation~\ref{eq:model_1_apparent_rate_density}), 
except for the radius dependence and normalization.
As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.
If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
density for singles becomes quite simple:
\begin{align}
\left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r}
&=
\frac{1 + 2^{\frac{\delta+3}{2}}\mu}{1 + \mu}.
\label{eq:power_law_correction}
\end{align}
If the binary fraction $0.1$, $\mu\approx 0.15$. Taking $\delta=-2.92$ from 
\citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
1.004$.
In other words, the apparent rate density is an {\it over}estimate compared to 
the rate density of single stars, with a relative difference $\delta \Gamma_0 
= |\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
This is quite a small effect!
Note though that it could change if the $Z_i$'s are not equal.
Also, the power law radius distribution $f(r) \propto r^\delta$ diverges for 
$\delta < 0$; \citet{howard_planet_2012}'s results indicate that this
approximation is good for $r\a\gtrsim 2r_\oplus$.
Similarly, it is nonsensical for $f(r)$ to be finite above some upper radius 
limit $r_u$, perhaps around $\approx 24r_\oplus$, based on the most inflated 
hot Jupiters.
An upper cut-off of $r_u$ would lead to smaller values of $\Gamma(r\a)$ 
down to $r_u/\sqrt{2}$, compared to an intrinsic power law without the cut-off.
We are not particularly interested in this effect; there are better 
models for hot Jupiter occurrence rates that we will discuss in 
Section~\ref{sec:further_models}.
If the assumptions behind this model (listed in 
Section~\ref{sec:general_formula}) are at all applicable in real transit surveys, 
this suggests that for $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$, 
binarity's impact on derived occurrence rates is quite small.

@@

We are mostly interested in the apparent rate density's radius dependence.
Marginalizing Equation~\ref{eq:general_Gamma_a} over apparent stellar mass, we 
find
that when $Z_0=Z_1=Z_2$,
\begin{align}
X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r} \\
&=
\notag
\frac{1}{1+\mu}
\left[1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
\left(
\int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
\right.
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
\left.\left.
\int_0^1 {\rm d}q\,q^{\beta+\delta+\frac{5}{3}} 
(1+q^\alpha)^{\frac{3}{2}}
(1+q^{-\alpha})^{\frac{\delta+1}{2}}
\right)\right],
\label{eq:powerlaw_vary_binary}
\end{align}
where $\gamma$ does not appear because of the marginalization over $M\a$.
For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give 
$(\ldots)\approx 
1.50249$. %171211_model_integrals.nb
For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
relative difference between the apparent rate density and the rate density 
around singles is 4.8\%.
This indicates that considering only twin binaries gave us correct 
intuition: for a power-law radius distribution 
($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
number of planets orbiting singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level.
